---
title: "Antibody responses to the BNT162b2 mRNA vaccine in individuals previously infected with SARS-CoV-2"
author: Min Wu, Nancy Sun
output: html_notebook
---

```{r packages, echo=F}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(tableone)
```

Valid antibody results at each visit:
•	Baseline: before vaccination or up to 3 days after vaccine dose #1
•	After Dose 1: 7-21 days after dose 1
•	After Dose 2: 7-21 days after dose 2

History of COVID criteria:
•	IgG N >= 1.4 at baseline or
•	Self-reported prior COVID or
•	Confirmed COVID positive PCR test in EHR (date precedes vaccine #1 date)
•	If self-reported prior COVID & IgG N < 1.4 at baseline & no positive PCR test in electronic health records, clinician reviewed medical charts for COVID history

Substantial Symptoms criteria:
•	Moderate to severe in degree and lasting <2 days, or
•	Of any severity and lasting >2 days


## Table 1: Characteristics of the Study Cohort

```{r table 1}
# Reformatting data for tables ------------------------------------------------

# by visit table
tab_dat <- antibody_df %>% # numeric antibody results for all antibody tests
  pivot_wider(names_from = test, values_from = value) %>%
  left_join(vac_dates, by="cs_mrn") %>% # dates of vaccination of survey participants
  left_join(survey_few, by="cs_mrn") %>% # survey responses of variables of interest
  # only including antibody results within timeframe specified above
  mutate(days1 = as.numeric(difftime(draw, as.Date(vac1), units = "days")),
         days2 = as.numeric(difftime(draw, as.Date(vac2), units = "days")),
         valid = case_when(
           visit == "Vaccine Dose 1"  & days1 < 3 ~ TRUE,
           visit == "Vaccine Dose 2" & days1 >= 7 & days1 <= 21 ~ TRUE,
           visit == "Post Vaccine 2 week" & days2 >= 7 & days2 <= 21 ~ TRUE,
           TRUE ~ FALSE
           )) %>%
  filter(valid) %>%
  select(-c(numvisit,draw,vac1,vac2,valid,days1,days2)) %>%
  # Readjustment of prior COVID based on criteria above
  mutate(had_covid = ifelse(cs_mrn %in% covid_pos_mrn$cs_mrn, "Yes", had_covid), # IgG N >= 1.4 at baseline or confirmed COVID positive PCR test
         had_covid = ifelse(cs_mrn %in% covid_reinfection$cs_mrn, "No", had_covid), # Covid after vaccine #1 date
         had_covid = ifelse(cs_mrn %in% no_covid_chartreviewed, "No", had_covid), # Chart reviewed patients for COVID history
         had_covid = replace_na(had_covid,"No")) %>%
  distinct()
  

# overall table (collapsing visits)
all_tab_dat <- tab_dat %>%
  group_by(cs_mrn) %>%
  mutate(`Architect IgG Index (S/C)` = mean(`Architect IgG Index (S/C)`),
         `Architect IgM Index (S/C)` = mean(`Architect IgM Index (S/C)`),
         `Architect Quant IgG II (AU/mL)` = mean(`Architect Quant IgG II (AU/mL)`)) %>%
  ungroup() %>%
  select(-visit) %>%
  distinct()


# Creating and joining tables --------------------------------

# variables for table
vars <- colnames(tab_dat)[-c(1,2)]

# demographic table broken down by visits (pre-vax, post-vax1, post-vax2)
sp_demo <- CreateTableOne(vars = vars, 
                          strata = "visit", 
                          tab_dat, 
                          includeNA = T)

# overall demographic table
all_demo <- CreateTableOne(vars = vars, 
                           data = all_tab_dat, 
                           includeNA = T)

# putting it all together and formatting
all_demo %>%
  print(format = "fp", explain = F, varLabels = T, test = T, missing = F, quote = F, noSpaces = T, printToggle = F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() %>%
  mutate(rowname = str_replace(rowname, " = TRUE", "")) %>%
  cbind(sp_demo %>%
          print(format = "fp", explain = F, varLabels = T, test = T, missing = F, quote = F, noSpaces = T, printToggle = F) %>%
          as_tibble(rownames = NA) %>%
          rownames_to_column() %>%
          mutate(rowname = str_replace(rowname, " = TRUE", "")) %>%
          select(-rowname))
```


## Data Formatting
```{r}
analysis_df <- byvisit_df %>%
  mutate(
    # create binary antibody result variables using threshold given by Abbott
    # Architect IgG Index (S/C)
    igg_n_pos = case_when(
      igg_n >= 1.4 ~ "Positive",
      igg_n < 1.4 ~ "Negative"
    ),
    # Architect IgM Index (S/C)
    igm_s_pos = case_when(
      igm_s >= 1.00 ~ "Positive",
      igm_s < 1.00 ~ "Negative"
    ),
    # Architect Quant IgG II (AU/mL)
    igg_s_pos = case_when(
      igg_s >= 50 ~ "Positive",
      igg_s < 50 ~ "Negative"
    ),
    # Architect Quant IgG II (AU/mL) - neutralizing antibody equivalent level >= 4160 AU/mL
    igg_s_neutral = case_when(
      igg_s >= 4160 ~ ">= 4160 AU/mL",
      igg_s < 4160 ~ "< 4160 AU/mL"
    ),
    # ACE2 Binding (%) 50%
    ace_50 = ace >= 50,
    # (natural) log transform antibody results due to skewed distribution
    log_igg_n = log(igg_n), 
    log_igm_s = log(igm_s),
    log_igg_s = log(igg_s),
    # determine prior COVID status 
    reported_covid = (srv_health_covid_suspect.factor %in% c("Yes, I have had a positive test", "Yes, medical diagnosis but no test") & is.na(covid_dt)) | (!is.na(covid_dt) & covid_dt < dose_1), 
    # clinician adjudicated no history of COVID
    adj_no_covid = cs_mrn %in% c("598", "1080", "1354", "1425", "1567", "1621", "1705", "1748"),
    had_covid = replace_na(!adj_no_covid & (reported_covid | igg_n_1 >= 1.40), F),
    had_covid = factor(if_else(
      had_covid, "Prior COVID-19 infection", "No prior COVID-19 infection"
    )),
    # calculate duration between blood draw & vaccines
    days_vac1 = as.numeric(difftime(draw, dose_1, units = "days")),
    days_vac2 = as.numeric(difftime(draw, dose_2, units = "days")),
    # only include antibody results within the time frame specified above
    valid = case_when(
      visit == "1"  & days_vac1 < 3 ~ TRUE,
      visit == "2" & days_vac1 >= 7 & days_vac1 <= 21 ~ TRUE,
      visit == "3a" & days_vac2 >= 7 & days_vac2 <= 21 ~ TRUE,
      TRUE ~ FALSE
    ),
    visit_name = case_when(
      visit == "1" ~ "Baseline",
      visit == "2" ~ "After Dose 1",
      visit == "3a" ~ "After Dose 2"
    ),
    visit_name = factor(visit_name, ordered=T, levels=c("Baseline", "After Dose 1", "After Dose 2")),
    across(c("igg_n_pos", "igm_s_pos", "igg_s_pos", "igg_s_neutral", "ace_50"), factor)
  ) %>%
  filter(valid)
```

## Sensitivity analysis: Participants with 3 valid blood draws
```{r}
all3v_df <- analysis_df %>%
  group_by(cs_mrn) %>%
  filter(any(visit == "3a") & any(visit == "1") & any(visit == "2")) 
```

## Participants COVID+ after vaccine 1
```{r}
new_covid_df <- analysis_df %>%
  filter(!had_covid) %>%
  mutate(new_covid = !is.na(covid_dt) & covid_dt > dose_1) 
```

## Table S1: Comparison of antibody levels between participants with and without prior COVID-19 infection at matched time points
```{r}
s1_v1 <- analysis_df %>%
  filter(visit == "1") %>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

s1_v2 <- analysis_df %>%
  filter(visit == "2") %>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

s1_v3a <- analysis_df %>%
  filter(visit == "3a") %>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

tab_s1 <- bind_rows(s1_v1, s1_v2, s1_v3a) 
```

## Table S2: Comparison of antibody levels between participants with and without prior COVID-19 infection at shifted time points
•	prior covid baseline vs. no covid after dose 1
•	prior covid after dose 1 vs. no covid after dose 2
```{r}
shifted_timept <- analysis_df %>%
  mutate(
    dose1_levels = case_when(
      had_covid & visit == 1 ~ 1,
      !had_covid & visit == 2 ~ 2),
    dose2_levels = case_when(
      had_covid & visit == 2 ~ 1,
      !had_covid & visit == "3a" ~ 2,
    )
  )

dose1 <- shifted_timept %>%
  filter(!is.na(dose1_levels))%>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "dose1_levels", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

dose2 <- shifted_timept %>%
  filter(!is.na(dose2_levels))%>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "dose2_levels", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

tab_s2 <- bind_rows(dose1, dose2)
```

## Table S3: Sensitivity analysis comparing antibody levels between participants with and without prior COVID-19 infection at matched time points
Participants with all 3 visits (baseline, after dose 1 & after dose 2)
```{r}
s3_v1 <- all3v_df %>%
  filter(visit == "1") %>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

s3_v2 <- all3v_df %>%
  filter(visit == "2") %>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

s3_v3a <- all3v_df %>%
  filter(visit == "3a") %>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

tab_s3 <- bind_rows(s3_v1, s3_v2, s3_v3a) 
```

## Table S4: Sensitivity analysis comparing antibody levels between participants with and without prior COVID-19 infection at shifted time points
Participants with all 3 visits (baseline, after dose 1 & after dose 2)
```{r}
shifted_timept_3v <- all3v_df %>%
  mutate(
    dose1_levels = case_when(
      had_covid & visit == 1 ~ 1,
      !had_covid & visit == 2 ~ 2),
    dose2_levels = case_when(
      had_covid & visit == 2 ~ 1,
      !had_covid & visit == "3a" ~ 2,
    )
  )

dose1_3v <- shifted_timept_3v %>%
  filter(!is.na(dose1_levels))%>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "dose1_levels", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

dose2_3v <- shifted_timept_3v %>%
  filter(!is.na(dose2_levels))%>%
  CreateTableOne(vars = c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), strata = "dose2_levels", data = ., addOverall = F) %>%
  print(nonnormal= c("log_igg_s", "log_igg_n", "log_igm_s", "ace"), showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 0, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

tab_s4 <- bind_rows(dose1_3v, dose2_3v)
```

## Table S5: Comparison of proportions (%) of Anti-Spike Receptor Binding Domain IgG antibody levels >= 4160 AU/mL between participants with and without prior COVID-19 infection
```{r}
s5_v1 <- analysis_df %>%
  filter(visit == "1") %>%
  CreateTableOne(vars = "igg_s_neutral", strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= igg_s_neutral, showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 1, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

s5_v2 <- analysis_df %>%
  filter(visit == "2") %>%
  CreateTableOne(vars = "igg_s_neutral", strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= igg_s_neutral, showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 1, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

s5_v3a <- analysis_df %>%
  filter(visit == "3a") %>%
  CreateTableOne(vars = "igg_s_neutral", strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= igg_s_neutral, showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 1, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

tab_s5 <- bind_rows(s5_v1, s5_v2, s5_v3a) 
```

## Table S6. Comparison of proportions (%) of ACE2 binding >=50% between participants with and without prior COVID-19 infection
```{r}
s6_v2 <- analysis_df %>%
  filter(visit == "2") %>%
  CreateTableOne(vars = "ace_50", strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= ace_50, showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 1, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

s6_v3a <- analysis_df %>%
  filter(visit == "3a") %>%
  CreateTableOne(vars = "ace_50", strata = "had_covid", data = ., addOverall = F) %>%
  print(nonnormal= ace_50, showAllLevels = F, format = "fp", varLabels = T, dropEqual = T, catDigits = 1, contDigits = 1, pDigits = 3, explain = F, test = T, missing = F, quote = F, noSpaces = T, printToggle=F) %>%
  as_tibble(rownames = NA) %>%
  rownames_to_column() 

tab_s6 <- bind_rows(s6_v2, s6_v3a) 
```

## Symptoms data
```{r symptoms data}
# Reformatting and adjusting symptom responses
symp_tab <- symptoms_dat %>%
  filter(Symptom != "injection_site") %>%
  # symptoms if they had moderate/sev <2 days or any symptoms after 2 days
  mutate(anysymp = ifelse( Severity %in% c("Moderate","Severe+") |
                           Timing %in% c("<= 1 week", "> 1 week"),
                          "1","0"),
         symp = anysymp) %>%
  group_by(cs_mrn, visit) %>%
  mutate(anysymp=max(anysymp)) %>%
  ungroup() %>%
  select(-Timing, -Severity) %>%
  distinct() %>%
  pivot_wider(names_from = Symptom, values_from = symp) %>%
  mutate_at(-c(1,2,3), ~fct_recode(.,"Yes"="1", "No"="0")) %>%
  # including label of covid history
  left_join(tab_dat %>% select(cs_mrn, had_covid), by="cs_mrn") %>%
  # adding group label for comparison later...
  mutate(group = case_when(visit=="Vaccine Dose 1" & had_covid=="Yes" ~ "covid_v1",
                           visit=="Vaccine Dose 2" & had_covid=="No"  ~ "nocovid_v2"))
```

## Table S7: Significant post-vaccine symptoms by SARS-CoV-2 infection status following dose 1 and dose 2 of mRNA vaccine
```{r}
CreateTableOne(vars="anysymp", strata = "had_covid", subset(symp_tab,visit=="Vaccine Dose 1"), includeNA = F) 
CreateTableOne(vars="anysymp", strata = "had_covid", subset(symp_tab,visit=="Vaccine Dose 2"), includeNA = F) 
```

## Table S8: Significant post-vaccine symptoms following first and second mRNA vaccine doses by SARS-CoV-2 infection status
```{r}
CreateTableOne(vars="anysymp",
               strata = "group", 
               subset(symp_tab,!is.na(group)), 
               includeNA = F) %>% 
  print(format = "fp", explain = F, varLabels = T, test = T, missing = F, quote = F, noSpaces = T, printToggle = F) %>%
  as.tibble(rownames=NA) %>%
  rownames_to_column()
```

## Table S9: Significant post-vaccine symptoms by dose (first and second) of mRNA vaccine stratified by prior SARS-CoV-2 infection status
```{r}
# Chi-sq tests ------------
CreateTableOne(vars="anysymp", strata = "visit", subset(symp_tab,had_covid=="No"), includeNA = F) 
CreateTableOne(vars="anysymp", strata = "visit", subset(symp_tab,had_covid=="Yes"), includeNA = F) 

# Mcnemar Chi-sq tests --------
symp_tab %>% filter(had_covid=="No") %>%
  select(cs_mrn, visit, anysymp) %>%
  pivot_wider(names_from = visit, values_from = anysymp) %>%
  select(-cs_mrn) %>%
  mutate(`Vaccine Dose 1` = ifelse(`Vaccine Dose 1`==0, "no symp", "symp"),
         `Vaccine Dose 2` = ifelse(`Vaccine Dose 2`==0, "no symp", "symp")) %>%
  table %>%
  mcnemar.test()

symp_tab %>% filter(had_covid=="Yes") %>%
  select(cs_mrn, visit, anysymp) %>%
  pivot_wider(names_from = visit, values_from = anysymp) %>%
  select(-cs_mrn) %>%
  mutate(`Vaccine Dose 1` = ifelse(`Vaccine Dose 1`==0, "no symp", "symp"),
         `Vaccine Dose 2` = ifelse(`Vaccine Dose 2`==0, "no symp", "symp")) %>%
  table %>%
  mcnemar.test()
```

## Table S10: Types of symptoms reported following vaccine dose 1, by prior SARS-CoV-2 infection status
```{r}
CreateTableOne(vars = colnames(symp_tab)[-c(1,2,3,15,16)], 
               strata = "had_covid", 
               subset(symp_tab,visit=="Vaccine Dose 1"), 
               includeNA = F) %>% 
  print(format = "fp", explain = F, varLabels = T, test = T, missing = F, quote = F, noSpaces = T, printToggle = F) %>%
  as.tibble(rownames=NA) %>%
  rownames_to_column()
```

## Table S11: Types of symptoms reported following vaccine dose 2, by prior SARS-CoV-2 infection status. 
```{r}
CreateTableOne(vars = colnames(symp_tab)[-c(1,2,3,15,16)], 
               strata = "had_covid", 
               subset(symp_tab,visit=="Vaccine Dose 2"), 
               includeNA = F) %>% 
  print(format = "fp", explain = F, varLabels = T, test = T, missing = F, quote = F, noSpaces = T, printToggle = F) %>%
  as.tibble(rownames=NA) %>%
  rownames_to_column()
```

## Figure 1: IgG(S-RBd) antibody response to mRNA SARS-CoV-2 vaccination in individuals with and without prior SARS-CoV-2 infection
```{r}
fig_igg_s_covid <- analysis_df %>%
  filter(!is.na(had_covid)) %>%
  ggplot(aes(x=visit_name, y = log_igg_s, color = had_covid)) + 
  scale_color_manual(values = c("#1b7837", "#762a83")) +
  geom_boxplot(outlier.colour = NA, position = position_dodge(width=0.9)) + 
  geom_point(position=position_jitterdodge(dodge.width=0.9)) +
  theme_bw(base_size = 18) + 
  labs(
    x="Visit",
    y="ln(Architect Quant IgG II AU/mL)",
    colour="Had COVID"
  ) + 
  scale_y_continuous(breaks = seq(-6, 14, by=2), limits = c(-6, 14))
```

## Figure S1: Anti-Nucleocapsid Protein IgG Antibody Response to mRNA SARS-CoV-2 Vaccination in Persons With and Without Prior COVID-19 Infection
```{r}
fig_igg_n_covid <- analysis_df %>%
  filter(!is.na(had_covid)) %>%
  ggplot(aes(x=visit_name, y = log_igg_n, color = had_covid)) + 
  scale_color_manual(values = c("#1b7837", "#762a83")) +
  geom_boxplot(outlier.colour = NA, position = position_dodge(width=0.9)) + 
  geom_point(position=position_jitterdodge(dodge.width=0.9)) +
  theme_bw(base_size = 18) + 
  labs(colour='had_covid') + 
  ylab("ln(Architect IgG Index S/C)") +
  xlab("Visit") +
  scale_y_continuous(breaks = seq(-5, 3, by=2), limits = c(-5, 3))
```

## Figure S2: Anti-Spike Receptor Binding Domain IgG Antibody Response to mRNA SARS-CoV-2 Vaccination in Persons With and Without Prior COVID-19 Infection: Values Above and Below 4160 AU/mL
```{r}
fig_igg_s_neutral <- analysis_df %>%
  filter(!is.na(had_covid)) %>%
  ggplot(aes(x=visit_name, y = log_igg_s)) + 
  geom_boxplot(outlier.size = 0.1) + 
  geom_jitter(aes(color = fct_rev(igg_s_neutral)), position=position_jitter(0.1)) +
  theme_bw(base_size = 14) + 
  facet_wrap(~had_covid) +
  labs(color='Status') + 
  ylab("ln(Architect Quant IgG II AU/mL)") + 
  xlab("Visit")
```

## Figure S3: ACE2 Antibody Binding Capacity in Persons With and Without Prior COVID-19 Infection: Values Above and Below 50%
```{r}
fig_ace_50 <- analysis_df %>%
  filter(!is.na(ace) & !is.na(had_covid) & visit %in% c("2", "3a")) %>%
  ggplot(aes(x=visit_name, y = ace)) + 
  geom_boxplot(outlier.size = 0.1) + 
  geom_jitter(aes(color = fct_rev(ace_50)), position=position_jitter(0.1)) +
  theme_bw(base_size = 14) + 
  facet_wrap(~had_covid) +
  labs(color='Status') + 
  ylab("ACE2 Binding (%)") + 
  xlab("Visit")
```

